STAT 450 Project: Real Estate

### 2020-03-23 src/2nd_draft.Rmd
MSE and MSPE added. Reference fixed.

 - **Goodness of fit** is defined as the extent to which the sample data are consistent with the model, which examines how well the model explains the data. R-squared and adjusted R-squared are the most well-known measures of goodness of fit and higher R-squared and adjusted R squares indicate better goodness of fit.

 - **Prediction power** measures how well models can predict future values. Mean squared prediction power was used to compare the prediction performance across all of our fitted linear predictive models. To do that, the data set was divided into training data - used to build our models, and testing data - used to evaluate the prediction power of our models.

@@

Other than ordinary linear regressions, we are also interested in the performance of more advanced linear regressions like *Ridge* and *Lasso*. *Ridge* and *Lasso* have a different objective function to optimize; they take a penalty in the sum of absolute values and sum of squared absolute values of weights respectively. These models have an interesting characteristic, that is, a weight is assigned to each feature. This might be relevant to our study as the mill rate can be affected by each feature to a different extent. Also, another advantage of these models is that MSPE is more stable as the variance of MSPE is reduced. For more detials about the two models, please refer to the **References**.

@@

After the 50 runs, a vector of MSEs and a vector of MSPEs for each model were therefore constructed successfully. Based on these vectors, side-by-side boxplots were used to show the mean and the spread of MSE and MSPE across all models respectively. For more details about cross-validation, please refer to the **References**.

@@

For a detailed look at how the models were fitted and evaluated, please refer to the **Appendix**.

@@

>>>>

 - **Goodness of fit** is defined as the extent to which the sample data are consistent with the model, which examines how well the model explains the data. MSE (Mean Squared Error) is a measure of goodness of fit and a smaller MSE indicates better goodness of fit.

 - **Prediction power** measures how well models can predict future values. Mean squared prediction power was used to compare the prediction performance across all of our fitted linear predictive models. Prior to examine the prediction power, the data set was divided into training data - used to build our models, and testing data - used to evaluate the prediction power of our models. MSPE (Mean Squared Predction Error) on testing set is used to measure the prediction power in this study.

Refer to **Appendix** for forumlas of MSE and MSPE.

@@

Other than ordinary linear regressions, we are also interested in the performance of more advanced linear regressions like *Ridge* and *Lasso*. *Ridge* and *Lasso* have a different objective function to optimize; they take a penalty in the sum of absolute values and sum of squared absolute values of weights respectively. These models have an interesting characteristic, that is, a weight is assigned to each feature. This might be relevant to our study as the mill rate can be affected by each feature to a different extent. Also, another advantage of these models is that MSPE is more stable as the variance of MSPE is reduced. For more detials about the two models, please refer to **Appendix**.

@@

After the 50 runs, a vector of MSEs and a vector of MSPEs for each model were therefore constructed successfully. Based on these vectors, side-by-side boxplots were used to show the mean and the spread of MSE and MSPE across all models respectively. For more details about cross-validation, please refer to **Appendix**.

@@

@@

Measure of Goodness of Fit and Prediction Power:
https://channabasavagola.github.io/2018-01-09-metrics/
